%-------------------------
% Resume in Latex
% Author : Henry Qu
% License : MIT
%------------------------

\documentclass[letterpaper,11pt, english]{article}

\usepackage{latexsym}
\usepackage[english]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage[maxcitenames=10, minnames=3]{biblatex}
\usepackage[a4paper, top=2cm, bottom=2cm]{geometry}
\usepackage{csquotes} % smart and nestable quote marks
\usepackage{hyperref}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color} %\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
%\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
% \usepackage{tabularx}
% \usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{changepage} 
\usepackage{CJKutf8}
\usepackage{tabto}    % make nice tabbing
\usepackage{tabularx}
\usepackage[english]{datetime2}
\usepackage{datetime2-calc}
\usepackage{multirow}
\newcommand{\ExpandDTMdate}[1]{\DTMfetch{#1}{year}-\DTMfetch{#1}{month}-\DTMfetch{#1}{day}}
\input{glyphtounicode}
\setquotestyle{english}
\addbibresource[]{biblio.bib}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Yuanshuo Henry Qu} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:7324851243}{+1 732 485 1243}
    $|$
    \faAt \hspace{.5pt} \href{mailto:henry.yqu@gmail.com}{henry.yqu@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/henryyqu}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/QhenryQ}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Wakefield,+MA+01880/@42.5012174,-71.10937,13z/data=!3m1!4b1!4m6!3m5!1s0x89e37336b7b29abd:0x155bd497bd25ffef!8m2!3d42.5018307!4d-71.0750488!16zL20vMDFtMnBr?entry=ttu}{Wakfield, Massachusetts}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Rutgers University
      % \normalfont{(Admission rate: 0.09\%)}
      }{\textbf{New Brunswick, New Jersey}}
      {Ph.D. in Plant Breeding and Genetics; GPA: 3.8}{Sep 2014 \textbf{--} Oct 2020}
      {M.S.  in Statistics;   GPA: 3.9}{Sep 2015 \textbf{--} May 2017}
      {B.S.  in Plant Science;   GPA: 3.8}{Sep 2011 \textbf{--} May 2013}
    
    \resumeSubheading
      {Shanghai Jiao Tong University
      % \normalfont{(Admission rate: 0.85\%)}
      }{\textbf{Shanghai, China}}
      {B.E.  in Food Science and Engineering;   GPA: 3.2}{Sep 2008 \textbf{--} May 2011}
    
  \resumeSubHeadingListEnd



%----------- INDUSTRY EXPERIENCE -----------

\section{Industry Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Indigo Agriculture}{\textbf{Boston, Massachusetts}}
      {Senior Data Scientist}{Aug 2020 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Leveraged geospatial relationship and developed a statistical model that detects and labels irrigation events using on-farm temperature sensor data, enabling program scale-up by 261\%.}
            \resumeItem{Built predictive models for corn and soybean basis bids of ~3800 buyers across the United States, achieving model error standard deviation less than 8 cents for both crops.}
            \resumeItem{Improved diagnostic models for major corn- and soybean-producing counties and reduced error standard deviation by 23\% and 38\%, respectively. }
            \resumeItem{Hosted bi-weekly journal club on grain merchandising, sourcing, and sustainability topics. }
        \resumeItemListEnd
    
    \resumeSubheading
      {National Turfgrass Evaluation Program (NTEP)}{\textbf{Remote}}
      {Data and Statistical Consultant (part-time, 5hr/week)}{June 2022 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Formulate business problems to statistical questions that can be answered with NTEP's proprietary data}
            \resumeItem{Establish new or enhance existing trials and data collection protocols for better analysis results.}
            \resumeItem{Organize/participate in literature and grant reviews for NTEP and other grant-issuing entities.}
            \resumeItem{Fundraising and grant application}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- ACADEMIC EXPERIENCE -----------

\section{Academic Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Agronomy Journal}{\textbf{Remote}}
      {Associate Editor, Statistics and Agronomy}{Jan 2019 \textbf{--} Present}

    \resumeSubheading
      {Agrosystems, Geosciences \& Environmental Journal}{\textbf{Remote}}
      {Associate Editor, Statistics and Agronomy}{Jan 2019 \textbf{--} Present}

    \resumeSubheading
      {Rutgers Professional Turf Management School}{\textbf{New Brunswick, New Jersey}}
      {Instructor}{Jan 201 \textbf{--} Jan 2019}
        \resumeItemListStart
          \resumeItem{Designed course curriculum, lesson plans, and assessment tools.}
          \resumeItem{Organized and chaperoned field trips to encourage hands-on learning experiences.} 
          \resumeItem{Achieved 80\% or higher overall course evaluation scores for all four semesters taught.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- SKILLS -----------



\section{Skills}
\hspace{0.3cm}
    \begin{tabularx}{\textwidth}{@{}lX@{}}
      \textbf{Programing:} \hspace{0.1cm} & Python, R, STAN, BUGS, JAGS, SQL\\ 
        \\[-0.2cm] 
      \textbf{Tech:} \hspace{0.1cm} & Docker, Git, Linux, AWS\\
        \\[-0.2cm] 
      \textbf{Languages:} \hspace{0.1cm} & Mandarin Chinese (Native) English (Professional)\\
    \end{tabularx}

%----------- REFERENCES -----------

\section{Publications}
\subsection*{Journal Articles}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
    2023\hspace{1cm} &  \fullcite{groben2023mycobiome}\\
  \end{tabularx}
\end{flushleft}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
    2023 \hspace{1cm} & \fullcite{qu2023latent}\\
    \\[-0.2cm]
    2022 \hspace{1cm}  & \fullcite{morris2022improved} Meeting; online \\
    \\[-0.2cm]
    2021  & \fullcite{qu2022ros} \\
    \\[-0.2cm]
    2020  & \fullcite{qu2022redthread} \\
    \\[-0.2cm]
    2019  & \fullcite{qu2019finefescue} \\
    \\[-0.2cm]
    2018  & \fullcite{qu2018finfs} \\
  \end{tabularx}
\end{flushleft}


\subsection*{Book Chapters}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
  2023\hspace{1cm} &   \fullcite{2023considerations}
\end{tabularx}
\end{flushleft}

\subsection*{News Articles}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
  2021 \hspace{1cm} &   \fullcite{qu2021carbont} 
  \end{tabularx}
\end{flushleft}

\subsection*{Technical Reports}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
  2021 \hspace{1cm} &   \fullcite{qiu2021free-trade-zones}\\
  \\[-0.2cm]
  2019 \hspace{1cm} &   \fullcite{h2019pr}\\
  \\[-0.2cm]
  2016 \hspace{1cm} &   \fullcite{qu2016pry}\\
  \\[-0.2cm]
  2015 \hspace{1cm}&    \fullcite{qu2015pry}\\
\end{tabularx}
\end{flushleft}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
  2014 \hspace{1cm} &   \fullcite{qu2014pry}\\
  \\[-0.2cm]
    2018 \hspace{1cm} &   \fullcite{qu2018ptf}\\
  \\[-0.2cm]
  2017\hspace{1cm}  &   \fullcite{qu2017ptf}\\
  \\[-0.2cm]
  2019 \hspace{1cm}&    \fullcite{qu2019perftallfescue}\\
  \\[-0.2cm]
  2017\hspace{1cm}  &   \fullcite{qu2017perfryegrass}\\
  \\[-0.2cm]
  2018 \hspace{1cm} &   \fullcite{qu2018perfryegrass}\\
  \\[-0.2cm]
  2018 \hspace{1cm}&    \fullcite{qu2018perffinefescue}\\
  \\[-0.2cm]
  2019 \hspace{1cm} &   \fullcite{qu2019perffinefescue}\\
\end{tabularx}
\end{flushleft}

%----------- AWARDS & ACHIEVEMENTS -----------
\begin{comment}
\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500.} \\ \vspace{3pt}
        
        \textbf{KYK Outstanding Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK).} \\ \vspace{3pt}
        
        \textbf{Boğaziçi University Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University.} \\ \vspace{3pt}
        
        \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to undergraduate students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK).} \\ \vspace{3pt}
        
        % \textbf{Boğaziçi University English Proficiency Test (BUEPT):}{ Achieved the highest grade A on the BUEPT grading scheme with a total score in the range of 85-100.} \\ \vspace{3pt}
        
        \textbf{Kocaeli Science High School Salutatorian Award:}{ Graduated as the second-highest ranked student in my class.}
    }}
  \resumeSubHeadingListEnd
\end{comment}


%----------- PROJECTS -----------
\begin{comment}
\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Filters and Fractals} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch.}
            \resumeItem{Added recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle in PPM format.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Chess Bot} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move.}
            \resumeItem{Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Rocket Flight Simulator} $|$ \emph{\href{https://github.com/arasgungore/rocket-flight-simulator}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A Simulink project which can accurately simulate the motion of a flying rocket in one-dimensional space.}
            \resumeItem{The project implements the forces acting on a rocket which are drag, weight, and thrust as subsystems that take time-variant parameters into consideration such as distance from the center of Earth, mass and velocity of the rocket, and air density at different layers of Earth's atmosphere.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Netlist Solver} $|$ \emph{\href{https://github.com/arasgungore/netlist-solver}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A MATLAB project that uses modified nodal analysis (MNA) algorithm to calculate the node voltages of any analog circuit without dependent sources given in netlist format.}
            \resumeItem{Added a module that sweeps the resistance of a load resistor, plots power dissipation as a function of load resistance, and finds the resistance value corresponding to maximum power.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{CMPE 250 Projects} $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Five Java projects assigned for the Data Structures and Algorithms (CMPE 250) course in the Fall 2021-22 semester.}
            \resumeItem{These projects apply DS\&A concepts such as discrete-event simulation (DES) using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree (MST), Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd
  \end{comment}


%----------- SKILLS -----------



%----------- RELEVANT COURSEWORK -----------
\begin{comment}
\section{Relevant Coursework}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Major coursework:}{ Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering} \\ \vspace{3pt}
        
        \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms}
    }}
  \resumeSubHeadingListEnd
\end{comment}

\section{Presentations \& Talks}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
    2022--11--08 \hspace{1cm} & A Latent Scale Model to Minimize Subjectivity for Visual Rating Data in the National Turfgrass Evaluation Program (NTEP). 2022 ASA-CSSA-SSSA International Annual Meeting. Baltimore, MD \\
    \\[-0.2cm] 
    2022--07--12 \hspace{1cm} & Evaluation and genetic analysis of red thread (\textit{Laetisaria fuciformis}) disease prevalence in tall fescue (\textit{Festuca arundinacea}). The 14th International Turfgrass Research Conference (ITRC). Copenhagen, Denmark. \\
    \\[-0.2cm]
    2022--04--04 \hspace{1cm} & Rasch Scale Model and Its Application to NTEP data. Turfgrass Breeders Association Meeting; online \\
    \\[-0.2cm]
    2019--11--12 \hspace{1cm} & Genetic Analysis on Drought Response of Tall Fescue [\textit{Festuca arundinacea} (Schreb.)] in Rain-out Shelter Using Bayesian Mixed Linear Models. 2019 ASA-CSSA-SSSA International Annual Meeting. San Antonio, TX. \\
    \\[-0.2cm]
    2019--07--31 \hspace{1cm} & Breeding of Tall Fescue with Improved Drought Tolerance. 2019 Rutgers Turfgrass Research Field Days. Freehold, NJ. \\

  \end{tabularx}
\end{flushleft}
\begin{flushleft}
    \begin{tabularx}{\textwidth}{@{}lX@{}}
    2019--06--05 \hspace{1cm} & Turf Industry in the United States- from Research to Production. Invited Presentation to China Agricultural University. Beijing, China. \\
    \\[-0.2cm]
    2019--01--25 \hspace{1cm} & Estimation of Variance Components and Narrow Sense Heritability from Family Data under Bayesian Framework. 2019 Rutgers Plant Science Symposium. New Brunswick, NJ. \\
    \\[-0.2cm]
    2018--11--05 \hspace{1cm} & Application of Bayesian Statistics to Genotype Evaluation and Phenotypic Selection. 2018 ASA-CSSA-SSSA International Annual Meeting. Baltimore, MD. \\
  \end{tabularx}
\end{flushleft}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
2018--08--01 \hspace{1cm} & 2017 NTEP Tall Fescue Trial. 2018 Rutgers Turfgrass Research Field Days. Freehold, NJ. \\
\\[-0.2cm]
2017--07--21 \hspace{1cm} & Breeding Fine Fescues for Improved Shade Tolerance. 2017 International Turfgrass Research Conference, Rutgers Turfgrass Tour. Freehold, NJ. \\
\\[-0.2cm]
2017--02--27 \hspace{1cm} & Cool-Season Turfgrass Breeding and the Turf Industry in the United States. The New Jersey Institute of Technology, Innovation in Ag. Newark, NJ. \\
\\[-0.2cm]
2016--05--12 \hspace{1cm} & Disease Resistance Screening and Genetic Diversity in the 2012 NTEP Tall Fescue Test. 2016 Rutgers Turfgrass Research Field Days. Freehold, NJ. \\
\\[-0.2cm]
2015--12--16 \hspace{1cm} & Introduction to Cool-Season Turfgrass Breeding and the Golf Industry in the United States. Annual GCSAA Conference of China. Hainan, China. \\
\\[-0.2cm] 
2015--07--28 \hspace{1cm} & Selection of Tall Fescue Cultivars with Improved Resistance to Brown Patch and Red Thread Disease. 2015 Rutgers Turfgrass Research Field Days. North Brunswick, NJ. \\
\\[-0.2cm] 
2014--07--29 \hspace{1cm} & Breeding and Selection of Tall Fescue. 2014 Rutgers Turfgrass Research Field Days. North Brunswick, NJ. \\
  \end{tabularx}
\end{flushleft}

\section{Plant Variety Developed}
\begin{flushleft}
\begin{tabularx}{\textwidth}{@{}p{5cm}@{\hspace{1cm}}X@{}}
    \textit{Festuca arundinacea} “Honeymoon” & RHL2 in 2018 NTEP Tall Fescue Test \\
    \\[-0.2cm]
    \textit{Festuca arundinacea} "AH1" & 2018 NTEP Tall Fescue Test \\
    \\[-0.2cm]
    \textit{Festuca arundinacea} "AH2"  & 2018 NTEP Tall Fescue Test \\
    \\[-0.2cm]
    \textit{Festuca arundinacea} "HWP"  & \\
    \\[-0.2cm]
    \textit{Lolium perenne} "Pharaoh"  & 2016 NTEP Perennial Ryegrass Test \\
\end{tabularx}
\end{flushleft}

\section{Media Exposure}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
      2023--01--16 \hspace{1cm} & Episode 157. Journeys: Boys of the Chinese Educational Mission; Grating The Nutmeg \emph{\href{https://gratingthenutmeg.libsyn.com/157-journeys-boys-of-the-chinese-educational-mission }{\color{blue}Video}}\\ 
      \\[-0.2cm] 
      2022--11--11 \hspace{1cm} & Remembering the Chinese Educational Mission at the Connecticut Historical Society; Connecticut Public Radio; \emph{\href{https://www.ctpublic.org/show/where-we-live/2022-11-11/remembering-the-chinese-educational-mission-at-the-connecticut-historical-society}{\color{blue}Video}}\\
  \end{tabularx}
\end{flushleft}

\section{Academic Service}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
      2020 \hspace{1cm} & Mentor, Cook Researchers of Plant Science Program at Rutgers University \\
      \\[-0.2cm] 
      2020 \hspace{1cm} & Teaching Assistant, Intro to Python Data Analysis workshop at the 2020 ASA-CSSA-SSSA Annual Meeting \\
      \\[-0.2cm] 
      2019 \hspace{1cm} & Volunteer, Intro to Python Data Analysis workshop at the 2019 ASA-CSSA-SSSA Annual Meeting \\
      \\[-0.2cm] 
      2018 \hspace{1cm} & Volunteer, Turf Bowl at GCSAA Education Conference and Golf Industry Show \\
      \\[-0.2cm] 
      2017 \hspace{1cm} & Volunteer, NJLCA Landscape Industry Certification Exam \\
  \end{tabularx}
\end{flushleft}

\section{Social Service}
\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}p{3cm}@{\hspace{0.01cm}}X@{}}
    \multirow{3}{3cm}{2022--09--29\\ \hspace{0.6cm} to \\2023--07--30} & Exhibition Consultant and Volunteer for “Journeys \begin{CJK*}{UTF8}{gbsn}旅途\end{CJK*}: Boys of the Chinese Educational Mission” at Connecticut Historical Society Museum and Library, Hartford, Connecticut \emph{\href{https://chs.org/exhibition/journeys/ }{\color{blue}Link}}\\
  \end{tabularx}
\end{flushleft}

\vspace{0.3cm}

\section{Awards \& Soceity Memberships}

\begin{flushleft}
\begin{tabularx}{\textwidth}{@{}lX@{}}
    2015--Present \hspace{0.5cm} & Member, Crop Science Society of America \\
    \\[-0.2cm] 
    2015--Present & Member, International Turfgrass Society \\
    \\[-0.2cm] 
    2014--2019  & Member, New Jersey Turfgrass Association \\
    \\[-0.2cm] 
    2018--2019  & Member, New Jersey Landscape Contractors Association \\
\end{tabularx}
\end{flushleft}

\begin{flushleft}
  \begin{tabularx}{\textwidth}{@{}lX@{}}
    2014--2020 \hspace{1cm} & Member, Cook Researchers of Plant Science at Rutgers University \\
      \\[-0.2cm] 
      2020 \hspace{1cm} & Spencer Davis Award, Department of Plant Biology, Rutgers University \\
      \\[-0.2cm] 
      2019 \hspace{1cm} & New Jersey Turfgrass Foundation Hall of Fame Scholarship, New Jersey Turfgrass Foundation \\
      \\[-0.2cm] 
      2018 \hspace{1cm} & Dr. James Watson Fellowship, The Toro Company and the Environmental Institute for Golf (EIFG) of Golf Course Superintendents Association of America (GCSAA) \\
      \\[-0.2cm] 
      2018 \hspace{1cm} & New Jersey Landscape Contractors Association Scholarships, Landscape Contractors Association of New Jersey \\
      \\[-0.2cm] 
      2017 \hspace{1cm} & Golf Course Superintendents Association of New Jersey Scholarships, GCSANJ \\
      \\[-0.2cm] 
      2016 \hspace{1cm} & Ralph Geiger Scholarship, Center for Turfgrass Science \\
      \\[-0.2cm] 
      2015 \hspace{1cm} & Weston Memorial Scholarship, Center for Turfgrass Science \\
      \\[-0.2cm] 
      2014 \hspace{1cm} & NJ State Golf Association \& Ralph Engel Caddie Scholarship, New Jersey State Golf Association \\
  \end{tabularx}
\end{flushleft}
  


%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd

\begin{comment}
\section{Skills}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Programing:}{Python, R, STAN, BUGS, JAGS, SQL}
      {Python, R, STAN, BUGS, JAGS, SQL}{}

    \resumeSubheading
      {Tech:}{}
      {Docker, Git, Linux, AWS}{}

    \resumeSubheading
      {Languages:}{}
      {Mandarin Chinese (Native) English (Professional)}{}    
  \resumeSubHeadingListEnd
\end{comment}

\begin{comment}
  \section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Skills:}{ Python, R, STAN, BUGS, JAGS, SQL} \\ \vspace{3pt}
        
        \textbf{Tech:}{ Docker, Git, Linux, AWS} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Mandarin Chinese (Native) English (Professional)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd
\end{comment}

%-------------------------------------------
\end{document}
